Effects of CHILDREN's programs

### 2020-02-22 paper.Rnw
Started including first regression table from DiD in Rnw file

>>>>

<<echo=FALSE, results='asis'>>=
library(stargazer)
lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
# table1_selfworth <- 
stargazer(lm1_selfworth,
                    lm2_selfworth,
                    lm3_selfworth,
                    lm4_selfworth,
          title = "Regression Results",
          order = c('Constant', 'treatEF'),
          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
                   'dummy_2018', 'id'
                  ),
          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
          align = TRUE)
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

% table1_selfworth <- stargazer(lm1_selfworth,
%                     lm2_selfworth,
%                     lm3_selfworth,
%                     lm4_selfworth,
%           title = "Regression Results",
%           order = c('Constant', 'treatEF'),
%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
%                    'dummy_2018', 'id'
%                   ),
%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
%           align = TRUE)

% \begin{table}[!htbp] \centering 
%   \caption{Regression Results} 
%   \label{} 
% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-5} 
% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
% \hline \\[-1.8ex] 
%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
%   & & & & \\ 
%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
%   & & & & \\ 
% \hline \\[-1.8ex] 
% ID fixed effects & No & No & Yes & Yes \\ 
% Time fixed effects & No & Yes & No & Yes \\ 
% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

### 2020-02-22 paper.tex
Started including first regression table from DiD in Rnw file

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

For our empirical analysis we define a treatment and a control group. Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program. On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds. Children that benefit from

@@

The baseline of the empirical approach is the determination of the treatment and control group.

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'cowplot' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(`\_inherit`, env, NULL): object 'GeomCustomAnn' not found}}\end{kframe}

@@

@@

The baseline of the empirical approach is the determination of the treatment and control group. Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program. On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.

\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Please cite as:}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ R package version 5.2.2. https://CRAN.R-project.org/package=stargazer}}\end{kframe}
% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sat, Feb 22, 2020 - 8:34:59 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

% table1_selfworth <- stargazer(lm1_selfworth,
%                     lm2_selfworth,
%                     lm3_selfworth,
%                     lm4_selfworth,
%           title = "Regression Results",
%           order = c('Constant', 'treatEF'),
%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
%                    'dummy_2018', 'id'
%                   ),
%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
%           align = TRUE)

% \begin{table}[!htbp] \centering 
%   \caption{Regression Results} 
%   \label{} 
% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-5} 
% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
% \hline \\[-1.8ex] 
%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
%   & & & & \\ 
%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
%   & & & & \\ 
% \hline \\[-1.8ex] 
% ID fixed effects & No & No & Yes & Yes \\ 
% Time fixed effects & No & Yes & No & Yes \\ 
% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}
